babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-09 article.tex
Better

\verb;babette; has functionality of both Tracer and
DensiTree. Tracer, among others, shows the effective sample
sizes of each posterior's variables. As an MCMC run needs to
converge first, Tracer discards the first 10\% of all parameter
estimates. This is called the burn-in. To calculate the effective
sample sizes in \verb;babette;, with the same burn-in of 10\%:

@@

Tracer displays multiple summary statistics for each
estimated variable. To obtain, for example, the
summary statistics of the estimated birth rate in \verb;babette;:

@@

DensiTree displays the phylogenies in a posterior.
To do the same in \verb;babette;:

>>>>

\verb;babette; allows for the same functionality of Tracer. 
Tracer, among others, shows the effective sample
sizes of each posterior's variables. As an MCMC run needs to
converge first, Tracer discards the first 10\% of all parameter
estimates. This is called the burn-in. To calculate the effective
sample sizes in \verb;babette;, with the same burn-in of 10\%:

@@

Tracer displays multiple summary statistics for each
estimated variable: the mean and its standard error, standard deviation,
variance, median, mode, geometric mean, 95\% HPD interval, auto-correlation
time and effective sample size. To obtain all these summary statistics 
of the estimated birth rate in \verb;babette;:

@@

\verb;babette; allows for the same functionality of DensiTree.
DensiTree displays the phylogenies in a posterior at the same
time scale over one another, allowing to see the uncertainty in
topology and branch lengths. To vizualize the same in \verb;babette;:
